\hypertarget{john-brzezicki}{%
\section{John Brzezicki}\label{john-brzezicki}}

\hypertarget{web-developer}{%
\subsection{Web Developer}\label{web-developer}}

johnbrz@gmail.com

310-561-4509

650 Edith Way, Long Beach, CA 90807

\hypertarget{summary}{%
\subsubsection{Summary:}\label{summary}}

\begin{itemize}
\tightlist
\item
  Four years professional experience developing LAMP applications,
  managing Apache servers, and working with and within modern CMS
  frameworks;
\item
  Excellent ability to communicate with management, engineering, and
  customers;
\item
  Intelligent, curious, and enthusiastic problem-solver;
\item
  Friendly disposition, and overall great co-worker and addition to any
  office environment.
\end{itemize}

\hypertarget{experience}{%
\subsection{Experience:}\label{experience}}

\hypertarget{ecyberdeck-champions-cup-softball-tournament}{%
\subsubsection{eCyberDeck / Champions Cup Softball
Tournament}\label{ecyberdeck-champions-cup-softball-tournament}}

\hypertarget{contract-web-developer}{%
\subsubsection{Contract Web Developer}\label{contract-web-developer}}

\hypertarget{november-2012---june-2013-august-2015---present}{%
\subsubsection{November 2012 - June 2013 , August 2015 -
Present}\label{november-2012---june-2013-august-2015---present}}

\begin{itemize}
\tightlist
\item
  Coded functionality for multiple web applications in Javascript, PHP,
  XML, and the ModX Content Management System.
\item
  Designed, coded, and maintained a single-page web application to
  manage teams, update scores, and provide live results for an annual
  softball tournament attended by more than 400 players and personnel.
\item
  Wrote a softball playoff-seeding calculator that integrated with
  existing tournament system to reduce administrative time-cost per
  season.
\item
  Implemented the Active.com golf tee-time API to build a tee-time
  searcher and scheduler.
\item
  Focused on readability and maintainability of code.
\end{itemize}

\hypertarget{insight-designs-web-solutions-llc.}{%
\subsubsection{Insight Designs Web Solutions,
LLC.}\label{insight-designs-web-solutions-llc.}}

\hypertarget{lamp-developer-system-administrator}{%
\subsubsection{LAMP Developer, System
Administrator}\label{lamp-developer-system-administrator}}

\hypertarget{july-2014---august-2015}{%
\subsubsection{July 2014 - August 2015}\label{july-2014---august-2015}}

\begin{itemize}
\tightlist
\item
  Maintained dozens of web sites and servers across multiple
  environments, writing custom front-end and back-end code to fulfill
  customer requirements.
\item
  Installed, updated, maintained, and wrote custom code for Wordpress,
  Magento, and Drupal sites, including legacy sites with outdated
  codebase.
\item
  Communicated with clients personally to troubleshoot problems, offer
  solutions, and provide estimates on projects.
\item
  Wrote custom PHP and Bash scripts to launch scheduled tasks, maintain
  files, solve complicated formulas, and assess security
  vulnerabilities.
\item
  Acted as one of only a few technology experts, able to help coworkers
  and clients on other projects with a wide variety of technical issues.
\end{itemize}

\hypertarget{livngiv-inc.}{%
\subsubsection{LivnGiv, Inc.}\label{livngiv-inc.}}

\hypertarget{lamp-developer-system-administrator-tech-lead}{%
\subsubsection{LAMP Developer, System Administrator, Tech
Lead}\label{lamp-developer-system-administrator-tech-lead}}

\hypertarget{july-2013---july-2014}{%
\subsubsection{July 2013 - July 2014}\label{july-2013---july-2014}}

\begin{itemize}
\tightlist
\item
  Designed and maintained features for medium-scale LAMP application
  across multiple load-balanced AWS instances, used by several hundred
  users.
\item
  Acted as tech-lead, coordinating development with upper-management,
  and overseeing the work of two other developers.
\item
  Was responsible for system and database administration, keeping
  servers up-to-date and secure, as well as managing periodic data
  back-ups and system performance.
\item
  Improved-upon existing systems, including a web API that interfaced
  with iOS and Android mobile devices, and an employee-facing CMS for
  updating content easily.
\end{itemize}

\hypertarget{lazer-bearings}{%
\subsubsection{Lazer Bearings}\label{lazer-bearings}}

\hypertarget{co-founder}{%
\subsubsection{Co-founder}\label{co-founder}}

\hypertarget{june-2007---december-2008}{%
\subsubsection{June 2007 - December
2008}\label{june-2007---december-2008}}

\begin{itemize}
\tightlist
\item
  Built a skateboard-bearing business with a single other partner from
  the ground up, from initial conceptualization to placement in nine
  storefronts in the Los-Angeles area.
\item
  Participated in all aspects of maintaining and operating the business,
  from product and packaging design, manufacturer relations, and website
  design; to sales, event promotion, and customer service.
\item
  Planned and promoted a large-scale promotional event, The Art of
  Skateboarding, with live music, art gallery, a skateboard-ramp, and
  ten employees, which was attended by 500 people.
\end{itemize}

\hypertarget{education}{%
\subsection{Education:}\label{education}}

\hypertarget{university-of-california---santa-cruz}{%
\subsubsection{University of California - Santa
Cruz}\label{university-of-california---santa-cruz}}

\hypertarget{computational-mathematics-major}{%
\subsubsection{Computational Mathematics
Major}\label{computational-mathematics-major}}

\begin{itemize}
\tightlist
\item
  Completed third year of B.S. in Computational Mathematics, leaving
  school to start career.
\item
  Coursework focused on problem-solving and abstract thinking.
\item
  Relevant Courses: Programming in Java, Multi-variable Calculus,
  Advanced Linear Algebra, Real Analysis, Proofs and Problem-solving.
\end{itemize}

\hypertarget{skills-interests}{%
\subsection{Skills / Interests:}\label{skills-interests}}

\begin{itemize}
\tightlist
\item
  Back-end: Linux, Apache, MySQL, PHP, Git, Bash, Wordpress, Magento,
  Drupal
\item
  Front-end: HTML5/CSS3, Javascript/jQuery, Foundation/Bootstrap
  responsive frameworks, Smarty PHP Templating, Angular
\item
  10 years of hobby experience in web development prior to starting
  career.
\item
  10 years of Linux use, including Bash shell scripting, server/database
  administration, managing virtual machines, and general
  troubleshooting.
\item
  Fond interest in Math and Computer Science.
\item
  Codility Silver Certificate holder and Project Euler member.
\item
  Enjoys composing and performing music.
\item
  Conversational Polish speaker
\end{itemize}

Copyright 2017 John Brzezicki
